---
title: "Assignment 3 - Web data"
author: "Adrian Werner"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
---
  
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

<!-- Do not forget to input your Github username in the YAML configuration up there --> 

***

```{r, include = T}
library(rvest)
library(stringr)
library(tidyverse)
library(corpus)
library(tm)
library(dplyr)
library(stylo)
library(stopwords)
library(httr)
```

<br>

***


### Task 1 - Speaking regex [7 points in total]

a) Below is a messy string that contains data on IP addresses and associated regions as well as latitudes and longitudes. Use regular expressions to parse information from the string and store all variables in a data frame. Return the data frame. [5 points]

```{r}
ip_geolocated <- "24.33.233.189 Ohio 39.6062 -84.1695 55.206.140.56 Arizona 31.5552 -110.35 199.53.213.86 Zurich 47.3686 8.5391 85.114.48.220 Split-Dalmatia 43.0432 16.0875 182.79.240.83 Telangana 17.411 78.4487 98.65.172.56 Provence-Alpes-Cote d'Azur 43.2971 5.3668"

ipnum <- str_extract_all(ip_geolocated, "(\\d{2,3}[.]\\d{2,3}[.]\\d{2,3}[.]\\d{2,3})")

ip.address <- unlist(ipnum)

ip_geolocated2 <- str_remove_all(ip_geolocated,"(\\d{2,3}[.]\\d{2,3}[.]\\d{2,3}[.]\\d{2,3})")

locationid <- unlist(str_extract_all(ip_geolocated2, "[- ][0-9]{1,3}[.][0-9]{2,4}"))

longitudes <- locationid[seq(0, length(locationid), 2)]
latitudes <- locationid[seq(1, length(locationid), 2)]

ip_geolocated3 <- str_remove_all(ip_geolocated2, "[- ][0-9]{1,3}[.][0-9]{2,4}")

ip_geolocated3 <- str_split(ip_geolocated3," ")
ip_geolocated3 <- unlist(ip_geolocated3)
place <- ip_geolocated3[c(2,5,8,10,12,14)]

data.frame(place, ip.address, latitudes, longitudes)

```

<br>

b) The following code hides a secret message. Crack the complete message with R and regular expressions. Once you have cracked it, collapse the solution into one single string. [2 points]

```{r}
secret <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.RqoE65fGEa1otfb7wXm24k.6t3sH9zqe5fy89n6Ed5t9kc4fR905gmc4Ogxo5nhk!gr"

#Tbh, I have no idea what we are supposed to do here.

```

<br>

***

### Task 2 - Scraping newspaper headlines [13 points in total]

Use R to scrape the article headlines from https://www.theguardian.com/international. 

a) Construct an XPath expression (not using SelectorGadget, but your own) that captures the headline texts from the website. Then, apply it, report the number of unique headings, and provide a random sample of 5 observations from the vector of scraped headlines. [3 points]

```{r}
guardian_url <- "https://www.theguardian.com/international"
guard_html <- read_html(guardian_url)
  
#most headings
headings <- as.list(guard_html %>% 
  html_elements(xpath = '//div/div/div/h3') %>% 
  html_text2())

#very small headings
headings.2 <- as.list(guard_html %>% 
  html_elements(xpath = '//li/h4') %>% 
  html_text2())

#top 10
headings.3 <- as.list(guard_html %>% 
  html_elements(xpath = '//li/div/div/h3') %>% 
  html_text2())

allheadings <- c(headings, headings.2, headings.3)

#number of unique headings
length(unique(allheadings))

#random sample of 5
sample(allheadings, size = 5)

```


<br>

b) Identify the 5 most frequent words in all headlines, excluding English stopwords. Report their frequency. [3 points]

```{r}
all_words <- allheadings %>%
  str_split(" ") %>% 
  unlist()

#make them lowercase because stopwords are also 
all_words <- tolower(all_words)

#define stopwords and include "-"
stopwordslist <- c(stopwords("en", source = "snowball"), "–")

#delete stopwords
no_stopwords <- delete.stop.words(all_words, stop.words = stopwordslist)

#get frequency
table <- sort(table(no_stopwords), decreasing = TRUE) 
table %>%
  head()

```

<br>

c) Develop an XPath expression that locates the set of links pointing to the articles behind the headings from the previous tasks. Apply it to extract those links, storing them in a vector. Report the length of that vector; then, list the first 5 links. [3 points]

```{r}

url1 <- guard_html %>% 
  html_elements(xpath = '//div/div/div/h3') %>%
  html_nodes("a") %>%
  html_attr("href")

url2 <- guard_html %>% 
  html_elements(xpath = '//li/h4') %>%
  html_nodes("a") %>%
  html_attr("href")

url3 <- guard_html %>% 
  html_elements(xpath = '//li/div/div/h3') %>% 
  html_nodes("a") %>%
  html_attr("href")

allurls <- unique(c(url1, url2, url3))

length(allurls)

head(allurls, n = 5)
```

<br>

d) Provide polite code that downloads the article HTMLs to a local folder. Explain why your code follows best practice of polite scraping by implementing at least three practices (bullet points are sufficient). Provide proof that the download was performed successfully by listing the first 5 files in the folder and reporting the total number of files contained by the folder. Make sure that the folder itself is not synced to GitHub using `.gitignore`. [4 points]

```{r}

#disclaimer:  my code works fine and I downloads all articles in the folder #I assigned perfectly well. However, it does not download it as html, #explorer shows 'file'. Otherwise, everything works.


tempwd <- ("C:/Users/Hertie School/OneDrive - Hertie School/Introduction to Data Science/HTML")
dir.create(tempwd)
setwd(tempwd)

folder <- paste0(tempwd, "\\html_articles\\")
dir.create(folder)

for (url in allurls) {
    download.file(url, destfile = paste0(folder, basename(url)))
  Sys.sleep(runif(1, 0, 1))
}

#checking
list_files <- list.files(folder, pattern = "0.*")
list_files_path <- list.files(folder, pattern = "0.*", full.names = TRUE)
length(list_files)

#for some reason it only shows a ten but I downloaded all.

#staying identifiable
rvest_session <- session(guardian_url, 
  add_headers(`From` = "adwerner@gmx.de", 
              `UserAgent` = R.Version()$version.string))

#polite scraping

#I used Sys.sleep(runif(1, 0, 1) in order to to scrape at a speed that does #not cause trouble for the Guardian's server

#I stored data on my local drive first

#I am reachable via mail.

```
